Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-09 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Analyzing the Interaction between Knowledge and Social Commitment in Multi-Agent Systems]{Analyzing the Interaction between Knowledge and Social Commitments in Multi-Agent Systems}
\author{Faisal Al-Saqqar\\ \vspace{0.2cm} Supervised by: Dr. Jamal Bentahar}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{August 08, 2013}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Multi-Agent Systems MASs}
    \begin{frame}{Motivation}
    \begin{itemize}
    \item In concrete applications such as business settings, agents should reason on their knowledge and their social commitments at the same time, particularly when they are engaged in conversations.
    \item Examples:
     \begin{itemize}
      \item \textbf{NetBill payment protocol}.
      \item \textbf{The travel agent}.
      \item \textbf{The car rental company}.
     \end{itemize}
\end{itemize}
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{The NetBill payment protocol} \label{figure7}
\end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
\item \textbf{How to analyze the interaction between knowledge and social commitments in MASs?}.
\item There is \textbf{no formal framework and semantics} available in the
literature that allow us to reason about knowledge and social commitments in MASs at the same time.

@@

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we define a formal computational logic that can capture both knowledge and social commitments, so that properties involving both of them simultaneously can be expressed?}
        \begin{itemize}
         \item Combining logics of knowledge and commitments into one logic called Computation Tree Logic of Knowledge and Commitments (CTLKC).
        \end{itemize}
    \item \textbf{Is it enough to simply combine the current versions of knowledge and commitment logics?}
        \begin{itemize}
         \item Analyze the consistency of the CTLKC logic.
        \end{itemize}
    \item \textbf{What are the characteristics of the new logic that will combine knowledge and commitments?}
        \begin{itemize}
         \item The new logic should solve any inconsistency that might result from the combination of the two logics.
        \end{itemize}
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \begin{frame}{Multi-Agent Systems MASs}
%        \begin{itemize}
%            \itemsep=.35cm
%        	\item Multi-Agent System (MAS).
%            %\item Autonomous agents.
%        	\item Knowledge in MASs.
%            \item Social commitments in MASs.
%        \end{itemize}
%\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Knowledge in MASs}
    \begin{frame}{Knowledge in MASs}

        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Knowledge in MASs}.

             \begin{itemize}
              \item Hintikka and Lenzen.
              \item Kripke Models $M = (S, \{R_i\}_{i \in A}, V)$.
              \item Interpreted Systems.\\
              The formalism of interpreted systems is used to model the temporal evolution of a system of agents in order to reason about knowledge and temporal properties.\\
\textbf{Example:} ``Bob knows that it is sunny in Montreal".\\
This knowledge is denoted by $K_{Bob} \varphi$, where $\varphi$ means it is sunny in Montreal.
            \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Social commitments in MASs}
    \begin{frame}{Commitments in MASs}
        Agent Communication Languages (ACLs).
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Commitments in MASs}
            \begin{itemize}
              \item \textbf{Mental Approaches}. \\Agents can read each other minds.
              \item \textbf{Social Approaches}. \\
              Formally, $C_{i\rightarrow j}\varphi$ means that agent $i$, the debtor (that makes the commitment), commits to agent $j$, the creditor (towards which the commitment is made), that $\varphi$ (the content of the commitment) holds. \\
              \textbf{Example:}  A customer $Cus$ commits to send payment to a merchant $Mer$. This commitment is denoted by $C_{Cus \rightarrow Mer} \varphi$, where $\varphi$ means send payment.

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interpreted Systems}

    \begin{frame}{Interpreted Systems}
      \begin{itemize}
         \item A system is composed of a set of agents $ \mathcal{A}  =  \{  1, \dots, n  \} $.
         \item Each agent $i$ is described by:
                \begin{itemize}
                  \item A set of local states $L_i$.
                  \item A set of local actions $Act_i$.
                  \item A local protocol function $ P_i : L_i \rightarrow 2^{Act_i} $.
                  \item $ \tau_i $ is a local evolution function $ \tau_i : L_i \times Act_i \rightarrow L_i$.
                \end{itemize}
         \item ACT is the set of joint actions \\
          $ ACT = Act_1 \times \dots \times Act_n $
            \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Interpreted Systems}
    \begin{itemize}
    \item G is the set of all global states in the system \\
             $ G = L_1 \times \dots \times L_n$ is the Cartesian product of all local states of $n$ agents.
       \begin{itemize}
       \item A global state $ \mathfrak{g} = ( l_1, \dots,l_n) \in G$ represents a ``snapshot" of the system.
       \item The local state of agent $i$ in the global state $\mathfrak{g}$ is represented by the notation $ l_i(\mathfrak{g}) $.
       \end{itemize}
    \item The global evolution (transition) function can be defined as follows: $ \tau : G \times ACT \rightarrow G $.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Extended Interpreted Systems}

\begin{itemize}
\item El-Menshawy et al. and Bentahar et al. extended the formalism of interpreted systems.
    \begin{itemize}
    \item Each agent $i \in \mathcal{A}$ is associated with a set of local
variables $Var_i$.
    \item A shared variable exists between two agents $i$ and $j$ iff $ Var_i \cap Var_j \neq \emptyset$, which means the existence of communication channel between the two agents.
        \end{itemize}
\end{itemize}
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=.70 \columnwidth]{figures/figure8.png}
%%\includegraphics[scale=0.5]{figure1}
\caption{The NetBill payment protocol} \label{figure8}
\end{figure}

>>>>

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Cooperative Decision Making for Communities of Autonomous Web Services]{Cooperative Decision Making for Communities of Autonomous Web Services}
\author{Ehsan Khosrowshahi Asl\\ \vspace{0.2cm} Supervised by: \\Dr. Jamal Bentahar \\Dr. Hadi Otrok}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{December 17, 2013}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers 
        \item Community goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}.
        \begin{itemize}
            \item Most of the recent work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}.
        \begin{itemize}
            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
        \end{itemize}

@@

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we model and analyze the cooperation
        among the community members in realistic, applicable and practical
        settings?}
        \begin{itemize}
            \item Modeling the preference and valuation functions considering the worth of all subsets of players in realistic cooperative scenarios
            \item Solution concepts complexity issues
        \end{itemize}

\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \begin{frame}{Multi-Agent Systems MASs}
%        \begin{itemize}
%            \itemsep=.35cm
%        	\item Multi-Agent System (MAS).
%            %\item Autonomous agents.
%        	\item Knowledge in MASs.
%            \item Social commitments in MASs.
%        \end{itemize}
%\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Communities of Web Services}
    \begin{frame}{Community of Web Services}
        Communities of Web Services
        \begin{itemize}
            \item Ease and improve the process of Web services discovery in an open environment like the Internet
        	\item Improve service quality, availability and responsiveness
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Social commitments in MASs}
    \begin{frame}{Communities of Web Services}
        Communities of Web Services
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Communities of web services operations}
            \begin{itemize}
              \item Community Development
              \item Web Services Attraction and Retention
              \item Web Service Selection
            \end{itemize}                      	      	
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cooperative Game Theory}

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.   
         \begin{itemize}
            \item A set of tasks needs to be performed, they require different expertise.
            \item Agents do not have enough resource on their own to perform a task.
            \item Find complementary agents to perform the tasks.
            \begin{itemize}
                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}      
        \item \textbf{issues:}
            \begin{itemize}
                \item What coalition to form?
                \item How to reward each each member when a task is completed?
            \end{itemize}
      \end{itemize}
    \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{The classic problem}
    We have a population $N$ of $n$ agents.    
    \begin{definition} [Coalition]~\\
       A coalition $C$ is a set of agents: $C \in 2^N$.
        \begin{itemize}
            \item $N$ is the set of all agents (or players)
            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
        \end{itemize}
        \label {dfn:Coalition}
    \end{definition}

    \begin{itemize}        
        \item \textbf{problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
        \item \textbf{solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.

        \begin{itemize}
            \item What are the interesting properties that $x$ should satisfy?
            \item How to determine the payoff vector $x$?
        \end{itemize}

    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{An Example}

    \begin{center}
        $N = \{1,2,3\}$ \\
        $v(\{1\}) = 0, v(\{2\}) = 0, v(\{3\}) = 0$ \\
        $v(\{1,2\}) = 90, v(\{1,3\}) = 80, v(\{2,3\}) = 70$ \\
        $v(\{1,2,3\}) = 105$ \\
    \end{center}
